Outbreak response models of vaccine-preventable diseases in humans (1970-2019) - A systematic review

### 2023-06-21 analyses/scripts/orv_sys_rev_supplementary.Rmd
Removed separate rows operations as now being handled by data cleaning script

```{r echo=FALSE}
#count the number of unique diseases studied
disease_studied_by_outbreak_type <- data_without_fmd %>% 
  separate_rows(disease,  sep = ' ') %>% 
  mutate(disease = as_factor(disease), 
         outbreak_type = as_factor(str_replace(outbreak_type, ' ', '+'))
         ) %>% 
  group_by(disease) %>% 
  distinct(title, .keep_all = TRUE) %>% 
  count(disease, outbreak_type, sort = TRUE, name = 'num_of_studies') %>%
  pivot_wider(names_from = outbreak_type, values_from = 'num_of_studies') %>% 
  replace_na(list(hypothetical_outbreak = 0, real_outbreak = 0)) %>% 
  mutate(total = hypothetical_outbreak + real_outbreak) %>% 
  arrange(desc(total))

@@

```{r echo=FALSE}
#count the number of unique diseases studied
disease_studied_by_objective_type <- data_without_fmd %>% 
  separate_rows(disease,  sep = ' ') %>% 
  mutate(disease = as_factor(disease), 
         objectives = as_factor(objectives)
         ) %>% 
  group_by(disease) %>% 
  distinct(title, .keep_all = TRUE) %>% 
  count(disease, objectives, name = 'num_of_studies') %>%
  pivot_wider(names_from = objectives, values_from = num_of_studies) %>% 
  replace_na(list(future = 0, past = 0, both = 0)) %>% 
  mutate(total = future + past + both) %>% 
  arrange(desc(total))

@@

countries_studied_by_count <- data_without_fmd %>% 
    separate_rows(country_studied, sep = ' ') %>%
    distinct(title, country_studied, .keep_all = TRUE) %>% 
    count(collab_type, country_studied, name = 'num_of_studies', sort = T)

@@

# Connection of authors to the studied locations 
```{r}
author_location_count_by_disease <- data_without_fmd %>%
  separate_rows(disease, sep = ' ') %>% 
  mutate(author_in_country_studied = as_factor(author_in_country_studied), 
         disease = as_factor(disease)
         ) %>% 
  group_by(collab_type, disease) %>%
  distinct(title, .keep_all = TRUE) %>% 
  count(author_in_country_studied, sort = TRUE, name = "num_of_studies") %>% 
  complete(author_in_country_studied, fill = list(num_of_studies = 0)) %>% 
  pivot_wider(names_from = author_in_country_studied, values_from = num_of_studies) %>% 
  replace_na(list(yes = 0, no = 0, not_applicable = 0)) %>% 
  mutate(total = not_applicable + no + yes) %>% 
  ungroup(collab_type) %>% 
  arrange(desc(total))

>>>>

```{r echo=FALSE}
#count the number of unique diseases studied
disease_studied_by_outbreak_type <- data_without_fmd %>% 
  mutate(disease = as_factor(disease), 
         outbreak_type = as_factor(str_replace(outbreak_type, ' ', '+'))
         ) %>% 
  group_by(disease) %>% 
  distinct(title, .keep_all = TRUE) %>% 
  count(disease, outbreak_type, sort = TRUE, name = 'num_of_studies') %>%
  pivot_wider(names_from = outbreak_type, values_from = 'num_of_studies') %>% 
  replace_na(list(hypothetical_outbreak = 0, real_outbreak = 0)) %>% 
  mutate(total = hypothetical_outbreak + real_outbreak) %>% 
  arrange(desc(total))

@@

```{r echo=FALSE}
#count the number of unique diseases studied
disease_studied_by_objective_type <- data_without_fmd %>% 
  mutate(disease = as_factor(disease), 
         objectives = as_factor(objectives)
         ) %>% 
  group_by(disease) %>% 
  distinct(title, .keep_all = TRUE) %>% 
  count(disease, objectives, name = 'num_of_studies') %>%
  pivot_wider(names_from = objectives, values_from = num_of_studies) %>% 
  replace_na(list(future = 0, past = 0, both = 0)) %>% 
  mutate(total = future + past + both) %>% 
  arrange(desc(total))

@@

countries_studied_by_count <- data_without_fmd %>% 
    distinct(title, country_studied, .keep_all = TRUE) %>% 
    count(collab_type, country_studied, name = 'num_of_studies', sort = T)

@@

# Connection of authors to the studied locations 
```{r}
author_location_count_by_disease <- data_without_fmd %>%
  mutate(author_in_country_studied = as_factor(author_in_country_studied), 
         disease = as_factor(disease)
         ) %>% 
  group_by(collab_type, disease) %>%
  distinct(title, .keep_all = TRUE) %>% 
  count(author_in_country_studied, sort = TRUE, name = "num_of_studies") %>% 
  complete(author_in_country_studied, fill = list(num_of_studies = 0)) %>% 
  pivot_wider(names_from = author_in_country_studied, values_from = num_of_studies) %>% 
  replace_na(list(yes = 0, no = 0, not_applicable = 0)) %>% 
  mutate(total = not_applicable + no + yes) %>% 
  ungroup(collab_type) %>% 
  arrange(desc(total))
